---
title: "HW1"
author: "Zhao Tianxiao"
date: "2018/10/6"
output: pdf_document
---
# 1
```{r}
## Input
a <- "ACTC"
b <- "ACC"
alpha <- 1
beta <- -1
gamma <- -1

## Initialization
grade <- 0
final <- list()
aa <- as.vector(strsplit(a, ""))[[1]]
bb <- as.vector(strsplit(b, ""))[[1]]
score <- matrix(0, nrow = nchar(b)+1, ncol = nchar(a)+1)
index <- matrix(0, nrow = nchar(b)+1, ncol = nchar(a)+1)

## Computation; Index matrix represents the path
for(i in (1:nchar(b))){
  for (j in (1:nchar(a))){
    if (aa[j] == bb[i])
      grade = alpha
    else
      grade = gamma
    if( max(score[i, j] + grade, score[i, j+1] + beta, score[i+1, j] + beta) 
         == score[i, j] + grade && grade == alpha){
      score[i+1, j+1] = score[i, j] + grade
      index[i+1, j+1] = 3
    }
    else if( max(score[i, j] + grade, score[i, j+1] + beta, score[i+1, j] + beta) 
         == score[i, j] + grade && grade == gamma){
      score[i+1, j+1] = score[i, j] + grade
      index[i+1, j+1] = 4
    }
    else if( max(score[i, j] + grade, score[i, j+1] + beta, score[i+1, j] + beta) 
         == score[i, j+1] + beta){
      score[i+1, j+1] = score[i, j+1] + beta
      index[i+1, j+1] = 2
    }
    else if( max(score[i, j] + grade, score[i, j+1] + beta, score[i+1, j] + beta) 
         == score[i+1, j] + beta){
      score[i+1, j+1] = score[i+1, j] + beta
      index[i+1, j+1] = 1
    }
  }
}

## Reproduce the path
i = nchar(b)+1
j = nchar(a)+1
while (i>1 && j>1){
  if (index[i, j] == 3){
    i = i-1
    j = j-1
    final = c(list(c(i,j)), final)
  }
  else if (index[i, j] == 4){
    i = i-1
    j = j-1
  }
  else if(index[i, j] == 2){
    i = i-1
  }
  else if(index[i, j] == 1){
    j = j-1
  }
}
## Output: The score 
score[nchar(b)+1, nchar(a)+1]
```



# 2
```{r}
## Input
library(readr)
dd <- read_delim("LongestCommonSeq.txt", "\t", col_names = FALSE)
alpha <- 1
beta <- 0
gamma <- 0

## Initialization
final <- list()
result<- ""
a <- dd[[1]][1]
b <- dd[[1]][2]
aa <- as.vector(strsplit(dd[[1]][1], ""))[[1]]
bb <- as.vector(strsplit(dd[[1]][2], ""))[[1]]
score <- matrix(0, nrow = nchar(b)+1, ncol = nchar(a)+1)
index <- matrix(0, nrow = nchar(b)+1, ncol = nchar(a)+1)

## Computation; Index matrix represents the path
for(i in (1:nchar(b))){
  for (j in (1:nchar(a))){
    if (aa[j] == bb[i])
      grade = alpha
    else
      grade = gamma
    if( max(score[i, j] + grade, score[i, j+1] + beta, score[i+1, j] + beta) 
         == score[i, j] + grade && grade == alpha){
      score[i+1, j+1] = score[i, j] + grade
      index[i+1, j+1] = 3
    }
    else if( max(score[i, j] + grade, score[i, j+1] + beta, score[i+1, j] + beta) 
         == score[i, j] + grade && grade == gamma){
      score[i+1, j+1] = score[i, j] + grade
      index[i+1, j+1] = 4
    }
    else if( max(score[i, j] + grade, score[i, j+1] + beta, score[i+1, j] + beta) 
         == score[i, j+1] + beta){
      score[i+1, j+1] = score[i, j+1] + beta
      index[i+1, j+1] = 2
    }
    else if( max(score[i, j] + grade, score[i, j+1] + beta, score[i+1, j] + beta) 
         == score[i+1, j] + beta){
      score[i+1, j+1] = score[i+1, j] + beta
      index[i+1, j+1] = 1
    }
  }
}

## Reproduce the path
i = nchar(b)+1
j = nchar(a)+1
while (i>1 && j>1){
  if (index[i, j] == 3){
    i = i-1
    j = j-1
    final = c(list(c(i,j)), final)
  }
  else if (index[i, j] == 4){
    i = i-1
    j = j-1
  }
  else if(index[i, j] == 2){
    i = i-1
  }
  else if(index[i, j] == 1){
    j = j-1
  }
}

## Output: The score & the Longest Common Seq
score[nchar(b)+1, nchar(a)+1]
for(k in 1:score[nchar(b)+1, nchar(a)+1]){
  tempchar = as.character(bb[final[[k]][1]])
  result = paste(result, tempchar, sep = "")
}
result
```

The result is 'Bioinformatics is the application of information technology to the field of molecular biology. The term bioinformatics was coined by Paulien Hogeweg in 1979 for the study of informatic processes in biotic systems. Bioinformatics now entails the creation and advancement of databases, algorithms, computational and statistical techniques, and theory to solve formal and practical problems arising from the management and analysis of biological data. Over the past few decades rapid developments in genomic and other molecular research technologies and developments in information technologies have combined to produce a tremendous amount of information related to molecular biology. It is the name given to these mathematical and computing approaches used to glean understanding of biological processes. Common activities in bioinformatics include mapping and analyzing DNA and protein sequences, aligning different DNA and protein sequences to compare them and creating and viewing 3-D models of protein structures.'




